New lower bounds for Schur and weak Schur numbers

### 2021-04-07 article/article.tex
truc

Using a SAT solvers, we are able to exhibit adequate Schur partitions, i.e satisfying \(SE_+\) constraint, 
hence providing lower bound on \(SE_+\). We refer to such partition as \textit{templates}. Moreover, when using 
a template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.
\subsection{}

>>>>

Using a SAT solvers, we are able to exhibit adequate Schur partitions, i.e satisfying \(SE_+\) constraint, 
hence providing lower bound on \(SE_+\). We refer to such partition as \textit{templates}. Moreover, when using 
a template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperlink{SAT}{SAT section}. \\

The special case \(k \in {1, 2} \) provides Rowley's inequalities \hyperlink{label2}{\textbf{[2]}}, \(S(n+1) \geq 4S(n)+2\) and \(S(n+2) \geq 13S(n)+8\). 
In this case, \(SE_+(2) = 4 = S(2)\) and \(SE_+(3) = 13 = S(3)\). We found other inequalities as well.

\subsection{}
